taxize - taxonomic search and retrieval in R

### 2013-04-30 inst/doc/taxize_withcode.Rnw

\documentclass[letterpaper,superscriptaddress,showkeys,longbibliography,10pt]{revtex4-1}
\usepackage[utf8]{inputenc}
\usepackage{color,dcolumn,graphicx,hyperref}
\usepackage{natbib}
\usepackage{footnote}
\hypersetup
{
  colorlinks = true, linkcolor = blue, citecolor = blue, urlcolor = blue,
}

@@

## From GitHub
install_github("taxize_", "ropensci")
@

@@

<<phylomaticphylogeny, eval=TRUE, dev='png', out.width='.8\\linewidth', out.height='3in'>>=
library(doMC)
registerDoMC(cores=4)

# input the taxonomic names
taxa <- c("Poa annua", "Abies procera", "Helianthus annuus")

@@

# plot the tree
plot(tree, cex=1.2)
@

>>>>

\documentclass[letterpaper,superscriptaddress,showkeys,longbibliography,10pt]{revtex4-1}

\usepackage[utf8]{inputenc}
\usepackage{color,dcolumn,graphicx,hyperref}
\usepackage{natbib}
\usepackage{footnote}
\hypersetup
{
  colorlinks = true, linkcolor = blue, citecolor = blue, urlcolor = blue,
}

@@

## From GitHub
install.packages("devtools")
require(devtools)
install_github("taxize_", "ropensci")
@

@@

<<phylomaticphylogeny, eval=TRUE, dev='png', out.width='4in', out.height='4in', dpi=100>>=
# input the taxonomic names
taxa <- c("Poa annua", "Abies procera", "Helianthus annuus")

@@

# plot the tree
plot(tree, cex=1)
@

### 2013-04-30 inst/doc/taxize_withcode_appA.tex

\usepackage{alltt}
\usepackage[utf8]{inputenc}
\usepackage{color,dcolumn,graphicx,hyperref}
\usepackage{natbib}
\usepackage{footnote}
\hypersetup
{
colorlinks = true, linkcolor = blue, citecolor = blue, urlcolor = blue,
}

@@

\hlcomment{# Remove some fields}
(splist_tnrs <- splist_tnrs[, !\hlfunctioncall{names}(splist_tnrs) %in% \hlfunctioncall{c}(\hlstring{"matchedName"}, \hlstring{"annotations"}, 
    \hlstring{"uri"})])
\end{alltt}
\begin{verbatim}
           submittedName         acceptedName    sourceId score
3       Helanthus annuus    Helianthus annuus iPlant_TNRS  0.98
1         Pinos contorta       Pinus contorta iPlant_TNRS  0.96
4  Collomia grandiflorra Collomia grandiflora iPlant_TNRS  0.99
5       Abies magnificaa      Abies magnifica iPlant_TNRS  0.98
10       Rosa california     Rosa californica iPlant_TNRS  0.99
9         Datura wrighti      Datura wrightii iPlant_TNRS  0.98
7       Mimulus bicolour      Mimulus bicolor iPlant_TNRS  0.98
8       Nicotiana glauca     Nicotiana glauca iPlant_TNRS  1.00
6          Maddia sativa         Madia sativa iPlant_TNRS  0.97
2    Bartlettia scapposa   Bartlettia scaposa iPlant_TNRS  0.98
\end{verbatim}
\begin{alltt}

@@

\hlcomment{# So here's our updated species list}
(splist <- \hlfunctioncall{as.character}(splist_tnrs$acceptedName))
\end{alltt}
\begin{verbatim}
 [1] "Helianthus annuus"    "Pinus contorta"       "Collomia grandiflora"
 [4] "Abies magnifica"      "Rosa californica"     "Datura wrightii"     
 [7] "Mimulus bicolor"      "Nicotiana glauca"     "Madia sativa"        
[10] "Bartlettia scaposa"  
\end{verbatim}
\end{kframe}
\end{knitrout}

@@

\hlcomment{# Unfortunately, common names are not standardized like species names, so}
\hlcomment{# there are multiple common names for each taxon}
\hlfunctioncall{sapply}(comnames, length)
\end{alltt}
\begin{verbatim}
 [1] 3 3 3 3 3 3 3 3 3 3
\end{verbatim}
\begin{alltt}

@@

\hlcomment{# And we can make a data.frame of our scientific and common names}
(allnames <- \hlfunctioncall{data.frame}(spname = splist, comname = comnames_vec))
\end{alltt}
\begin{verbatim}
                 spname                       comname
1     Helianthus annuus              common sunflower
2        Pinus contorta                lodgepole pine
3  Collomia grandiflora        largeflowered collomia
4       Abies magnifica                    golden fir
5      Rosa californica           California wildrose
6       Datura wrightii            sacred thorn-apple
7       Mimulus bicolor yellow and white monkeyflower
8      Nicotiana glauca                  tree tobacco
9          Madia sativa                 coast tarweed
10   Bartlettia scaposa                Bartlett daisy
\end{verbatim}
\end{kframe}
\end{knitrout}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlcomment{# As we already have Taxonomic Serial Numbers from ITIS, let's just get}
\hlcomment{# classifications from ITIS. Note that we could use uBio instead.}
class_list <- \hlfunctioncall{classification}(tsns)
\hlfunctioncall{sapply}(class_list, nrow)
\end{alltt}
\begin{verbatim}
 [1] 12 11 12 11 12 12 12 12 12 12
\end{verbatim}
\begin{alltt}

@@

\hlcomment{# Now that we have allnames_df, we can start to see some relationships}
\hlcomment{# among species simply by their shared taxonomic names}
allnames_df[1:2, ]
\end{alltt}
\begin{verbatim}
              spname        comname Kingdom     Subkingdom Infrakingdom
1    Abies magnifica     golden fir Plantae Viridaeplantae Streptophyta
2 Bartlettia scaposa Bartlett daisy Plantae Viridaeplantae Streptophyta
      Division     Subdivision Infradivision         Class Superorder
1 Tracheophyta Spermatophytina  Gymnospermae     Pinopsida       <NA>
2 Tracheophyta Spermatophytina  Angiospermae Magnoliopsida  Asteranae
      Order     Family      Genus
1   Pinales   Pinaceae      Abies
2 Asterales Asteraceae Bartlettia
\end{verbatim}
\begin{alltt}

@@

\begin{figure}[!ht] 
\centering 
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlfunctioncall{library}(doMC)
\hlfunctioncall{registerDoMC}(cores = 4)  \hlcomment{# I have a mac, so using doMC package, use whatever you like}
phylogeny <- \hlfunctioncall{phylomatic_tree}(taxa = \hlfunctioncall{as.character}(allnames$spname), taxnames = TRUE, 
    get = \hlstring{"POST"}, informat = \hlstring{"newick"}, method = \hlstring{"phylomatic"}, storedtree = \hlstring{"R20120829"}, 
    taxaformat = \hlstring{"slashpath"}, outformat = \hlstring{"newick"}, clean = \hlstring{"true"}, parallel = TRUE)
phylogeny$tip.label <- \hlfunctioncall{capwords}(phylogeny$tip.label, onlyfirst = TRUE)
\hlfunctioncall{plot}(phylogeny)
\end{alltt}
\end{kframe}

{\centering \includegraphics[width=.8\linewidth,height=4in]{figure/phylogeny}

}

\end{knitrout}

@@

\begin{figure}[!ht] 
\centering 
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlfunctioncall{library}(doMC)
\hlfunctioncall{library}(rgbif)

@@

\hlcomment{# Make a map}
p <- rgbif::\hlfunctioncall{map}(occurr_list)
p
\end{alltt}
\end{kframe}

{\centering \includegraphics[width=\maxwidth,height=4in]{figure/map}

}

\end{knitrout}

>>>>

\usepackage{alltt}
\usepackage[utf8]{inputenc}
\usepackage{color,dcolumn,graphicx,hyperref}
\usepackage{natbib}
\usepackage{footnote}
\hypersetup
{
colorlinks = true, linkcolor = blue, citecolor = blue, urlcolor = blue,
}
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}

@@

\hlcomment{# Remove some fields}
(splist_tnrs <- splist_tnrs[, !\hlfunctioncall{names}(splist_tnrs) %in% \hlfunctioncall{c}(\hlstring{"matchedName"}, \hlstring{"annotations"}, 
    \hlstring{"uri"})])
\end{alltt}
\begin{verbatim}
data frame with 0 columns and 0 rows
\end{verbatim}
\begin{alltt}

@@

\hlcomment{# So here's our updated species list}
(splist <- \hlfunctioncall{as.character}(splist_tnrs$acceptedName))
\end{alltt}
\begin{verbatim}
character(0)
\end{verbatim}
\end{kframe}
\end{knitrout}

@@

\hlcomment{# Unfortunately, common names are not standardized like species names, so}
\hlcomment{# there are multiple common names for each taxon}
\hlfunctioncall{sapply}(comnames, length)

@@

\hlcomment{# And we can make a data.frame of our scientific and common names}
(allnames <- \hlfunctioncall{data.frame}(spname = splist, comname = comnames_vec))
\end{alltt}
\end{kframe}
\end{knitrout}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlcomment{# As we already have Taxonomic Serial Numbers from ITIS, let's just get}
\hlcomment{# classifications from ITIS. Note that we could use uBio instead.}
class_list <- \hlfunctioncall{classification}(tsns)
\hlfunctioncall{sapply}(class_list, nrow)

@@

\hlcomment{# Now that we have allnames_df, we can start to see some relationships}
\hlcomment{# among species simply by their shared taxonomic names}
allnames_df[1:2, ]

@@

\begin{figure}[!ht] 
\centering 
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
phylogeny <- \hlfunctioncall{phylomatic_tree}(taxa = \hlfunctioncall{as.character}(allnames$spname), taxnames = TRUE, 
    get = \hlstring{"POST"}, informat = \hlstring{"newick"}, method = \hlstring{"phylomatic"}, storedtree = \hlstring{"R20120829"}, 
    taxaformat = \hlstring{"slashpath"}, outformat = \hlstring{"newick"}, clean = \hlstring{"true"}, parallel = TRUE)
phylogeny$tip.label <- \hlfunctioncall{capwords}(phylogeny$tip.label, onlyfirst = TRUE)
\hlfunctioncall{plot}(phylogeny)
\end{alltt}
\end{kframe}
\end{knitrout}

@@

\begin{figure}[!ht] 
\centering 
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlfunctioncall{library}(rgbif)

@@

\hlcomment{# Make a map}
p <- rgbif::\hlfunctioncall{map}(occurr_list)
p <- p + \hlfunctioncall{guides}(col = \hlfunctioncall{guide_legend}(nrow = 2, byrow = TRUE)) + \hlfunctioncall{theme}(legend.position = \hlstring{"bottom"})
p
\end{alltt}
\end{kframe}
\end{knitrout}
